### 2016-06-08 paper.tex
기본 tex 파일 추가

\documentclass[a4paper,10pt]{article}

\usepackage{kotex}
\usepackage{datetime}
\usepackage{fullpage}
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{enumerate}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{float}
\usepackage{multirow}

\linespread{1.5}

\begin{document}

\section{haha}

TODO

\end{document}